---
title: "R Seurat Integration Notebook 1"
output: html_notebook
---


Load libraries:
```{r}
library(Seurat)
library(future)
options(future.globals.maxSize=990 * 1024^2)
library(dplyr)
```
Load data:
```{r}
controls=Read10X(data.dir = paste("/icgc/dkfzlsdf/analysis/B210/Luca/scRNA_test_015035/combined/combine_indexes/aggr_controls/outs/filtered_feature_bc_matrix/",sep=""))
treated=Read10X(data.dir = paste("/icgc/dkfzlsdf/analysis/B210/Luca/scRNA_test_015035/combined/combine_indexes/aggr_treated/outs/filtered_feature_bc_matrix/",sep=""))
```
Create Seurat objects and perfrom SC Transformation:
```{r}
 seu_list = c(controls,treated)
 annot_list = c("controls", "treated")

i=1  
  seu_list[[i]] <- CreateSeuratObject( seu_list[[i]], min.features = 100 )
  seu_list[[i]]@meta.data[,"sample"] <- annot_list[i]
  
  seu_list[[i]] <- PercentageFeatureSet(seu_list[[i]], pattern = "^mt-", col.name = "percent.mt")
  #high_mt_cells = names(seu_list[[i]]$nFeature_RNA[seu_list[[i]]$percent.mt >= 20])
  #seu_list[[i]] = subset(seu_list[[i]], cells = high_mt_cells, invert = TRUE)
  seu_list[[i]] <- subset(seu_list[[i]], subset = nFeature_RNA >= 800 & percent.mt < 20 )
  
  # SCTransform replaces NormalizeData, FindVariableFeatures, ScaleData
  # DO NOT run ScaleData after SCTransform
  seu_list[[i]] <- SCTransform(seu_list[[i]], verbose = FALSE, conserve.memory = FALSE, vars.to.regress = "percent.mt")

i=2

seu_list[[i]] <- CreateSeuratObject( seu_list[[i]], min.features = 100 )
  seu_list[[i]]@meta.data[,"sample"] <- annot_list[i]
  
  seu_list[[i]] <- PercentageFeatureSet(seu_list[[i]], pattern = "^mt-", col.name = "percent.mt")
  #high_mt_cells = names(seu_list[[i]]$nFeature_RNA[seu_list[[i]]$percent.mt >= 20])
  #seu_list[[i]] = subset(seu_list[[i]], cells = high_mt_cells, invert = TRUE)
  seu_list[[i]] <- subset(seu_list[[i]], subset = nFeature_RNA >= 300 & percent.mt < 20 )
  
  seu_list[[i]] <- SCTransform(seu_list[[i]], verbose = FALSE, conserve.memory = FALSE, vars.to.regress = "percent.mt")
```
Perform the integration of treated and controls:
```{r}
seu_features <- SelectIntegrationFeatures(object.list = seu_list, nfeatures = 3000)
seu_list <- PrepSCTIntegration(object.list = seu_list, anchor.features = seu_features, verbose = FALSE)

# considering 80 nearest neighbors when filtering anchors <- close to upper limit for smallest sample
anchors <- FindIntegrationAnchors(object.list = seu_list, normalization.method = "SCT", anchor.features = seu_features, verbose = FALSE, k.filter = 50)
seu <- IntegrateData(anchorset = anchors, normalization.method = "SCT", verbose = FALSE)
```

look at normalised data:
```{r}
seu[["integrated"]]@scale.data
seu[["integrated"]]@counts
seu[["integrated"]]@data
```
Run PCA:
```{r}
seu <- RunPCA(seu, features = VariableFeatures(seu))
```
Identify clusters and run UMAP:
```{r}
seu <-FindNeighbors(seu, dims = 1:10)
seu <- FindClusters(seu, resolution = 0.5)
seu <- RunUMAP(seu, dims = 1:10)
```
Plot UMAP reduction, labelling cells by cluster or by group:
```{r}
dimplot1=DimPlot(seu, reduction = "umap",label = 1)
seu$group=seu@meta.data[,"sample"]
#dimplot2=DimPlot(seu, reduction = "umap",label = 1,group.by = "group",cols=c("blue3","orange"))
dimplot2=DimPlot(seu, reduction = "umap",label = 1,split.by = "group")
#grid.arrange(dimplot1,dimplot2)
dimplot2
```

seu2=seu
seu2$group=factor(seu2$group,levels=c("controls","treated"))
#dimplot3=DimPlot(seu2, reduction = "umap",label = 1,group.by = "group",cols=c("blue3","orange"))
dimplot3=DimPlot(seu2, reduction = "umap",label = 1,group.by = "group",cols=c("red","cyan2"))

Save the plots:
```{r}
png(paste("~/Dim_plot_aggr_controls_treated_300_800.png",sep="_"),res = 600,width=12,height=10,units='in')
grid.arrange(dimplot1,dimplot3)
dev.off()
VlnPlot(seu, features = c( "Col1a1", "Col3a1", "Col5a1", "Col12a1", "Dcn", "Fbln2"),ncol = 2)
```
Identify markers across clusters:
```{r}
seu.markers <- FindAllMarkers(seu, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
top10 <- seu.markers %>% group_by(cluster) %>% top_n(n = 10, wt = avg_logFC)

id="aggr_control_treated"
threshold="300_800"
pct_mt=20

markers_filtmat=seu.markers[seu.markers$p_val_adj<0.05 & seu.markers$avg_logFC>=1,]
write.table(markers_filtmat,file=paste("~/Seurat",id,threshold,"selected_markers.csv",sep="_"),sep=",")
write.table(top10,file=paste("~/Seurat",id,threshold,"_top10_selected_markers.csv",sep="_"),sep=",")

clust_control_count=1:19
for (i in 0:18) { 
clust_control_count[i+1]=sum(seu$seurat_clusters[seu$group=="controls"]==i) 
}

clust_count=1:19
for (i in 0:18) { 
clust_count[i+1]=sum(seu$seurat_clusters==i) 
}
```
Identify markers between groups:
```{r}
markers_CT=FindMarkers(seu, ident.1="controls",group.by="group")

subsetC=subset(seu,cells=labels(seu$group[seu$group=="controls"]))
subsetT=subset(seu,cells=labels(seu$group[seu$group=="treated"]))
```
Look for genes in the selected features:
```{r fig.width=8, fig.height=5}
seu_features[grep("Pall",seu_features)]
```
markers1=c("Notch1","Notch4","Nav3") #c("Igfbp2","Odc1","Il17f","Notch1","Notch4","Nav3")

```{r fig.width=5, fig.height=7.5}
VlnPlot(seu, features = c( "Cd207" ,"Il1b","Il17f","S100a4"),ncol = 2,group.by = "group",pt.size = 0.2)
```

```{r fig.width=8, fig.height=7}
v1=VlnPlot(subsetC, features = markers1,ncol = 1)
v2=VlnPlot(subsetT, features = markers1,ncol = 1)

grid.arrange(arrangeGrob(v1,top =text_grob("controls",size=20  ) ) , arrangeGrob(v2,top =text_grob("treated", size=20) )  ,nrow=1)
```

png(paste("~/plot_seurat",id,threshold,pct_mt,"Vln_plot_markers_kerat_granular.png",sep="_"),res = 600,width=18,height=12,units='in')
VlnPlot(seu, features = c( "Flg2", "Lor"),ncol = 1)
dev.off()

png(paste("~/plot_seurat",id,threshold,pct_mt,"Vln_plot_markers_langerhans.png",sep="_"),res = 600,width=18,height=12,units='in')
VlnPlot(seu, features = c( "Cd207"),ncol = 1)
dev.off()

plot n_features across clusters: 

```{r fig.width=8, fig.height=6}
data2=data.frame(cluster=factor(seu$seurat_clusters),n_features=as.vector(seu$nFeature_SCT))
row.names(data2)=c()
ggplot(data=data2, aes(x=cluster,y=n_features))+geom_violin(aes(x=cluster,y=n_features,fill=cluster))
```

```{r}
VlnPlot(seu, features = c( "Gata3", "Tbx21"),ncol = 1)
```

```{r}
png(paste("~/plot_seurat",id,threshold,pct_mt,"Vln_plot_markers_CD4_helper.png",sep="_"),res = 600,width=18,height=12,units='in')
VlnPlot(seu, features = c( "Gata3", "Tbx21",  "Ccl4", "Cxcr6"),ncol = 1)
dev.off()

png(paste("~/plot_seurat",id,threshold,pct_mt,"Vln_plot_markers_CD4.png",sep="_"),res = 600,width=18,height=12,units='in')
VlnPlot(seu, features = c( "Cd4"),ncol = 1)
dev.off()

png(paste("~/plot_seurat",id,threshold,pct_mt,"Vln_plot_markers_CD8_exhausted.png",sep="_"),res = 600,width=18,height=12,units='in')
VlnPlot(seu, features = c( "Cxcl13", "Pdcd1", "Ctla4"),ncol = 1)
dev.off()

png(paste("~/plot_seurat",id,threshold,pct_mt,"Vln_plot_markers_CD8_naive.png",sep="_"),res = 600,width=18,height=12,units='in')
VlnPlot(seu, features = c( "Tcf7", "Ccr7", "Lef1", "Il7r", "Il6st", "Foxo1","Myc"),ncol = 1)
dev.off()

png(paste("~/plot_seurat",id,threshold,pct_mt,"Vln_plot_markers_memoryCD4_and_monocytes.png",sep="_"),res = 600,width=18,height=12,units='in')
VlnPlot(seu, features = c( "Cd14","Lyz2","S100a4"),ncol = 1)
dev.off()

png(paste("~/plot_seurat",id,threshold,pct_mt,"Feature_plot_markers_keratinocytes.png",sep="_"),res = 600,width=18,height=12,units='in')
FeaturePlot(seu, features =c("Krt5","Krt10","Krt14" ,"Ptgs1"),ncol=1)
dev.off()

png(paste("~/plot_seurat",id,threshold,pct_mt,"Vln_plot_markers_keratinocytes.png",sep="_"),res = 600,width=18,height=12,units='in')
VlnPlot(seu, features =c("Krt5","Krt10","Krt14" ,"Ptgs1"),ncol=1)
dev.off()

png(paste("~/plot_seurat",id,threshold,pct_mt,"Vln_plot_markers_epithelial.png",sep="_"),res = 600,width=18,height=12,units='in')
print(VlnPlot(seu, features = c( "Krt17", "Krt79", "Cd200", "Lrig1"),ncol = 1))
dev.off()

png(paste("~/plot_seurat",id,threshold,pct_mt,"Vln_plot_markers_stem.png",sep="_"),res = 600,width=18,height=12,units='in')
print(VlnPlot(seu, features = c( "Cd34", "Lgr5", "Lrig1", "Krt14"),ncol = 1))
dev.off()

png(paste("~/plot_seurat_",id,threshold,pct_mt,"_Vln_plot_markers_T_cytotoxic_Abdul.png",sep="_"),res = 600,width=18,height=12,units='in')
VlnPlot(seu, features = c( "Nkg7",  "Gzmb", "Ifng", "Prf1"),ncol = 2)
dev.off()

png(paste("~/plot_seurat_",id,threshold,pct_mt,"_Vln_plot_markers_cd4_T_helper_Abdul.png",sep="_"),res = 600,width=12,height=6,units='in')
VlnPlot(seu, features = c( "Gata3", "Tbx21", "Eomes", "Ccl4", "Ccl5", "Cxcr6"),ncol = 3)
dev.off()

png(paste("~/plot_seurat_",id,threshold,pct_mt,"_Feature_plot_markers_T_cytotoxic_Abdul.png",sep="_"),res = 600,width=12,height=6,units='in')
FeaturePlot(pbmc, features = c( "Nkg7",  "Gzmb", "Ifng", "Prf1"),ncol = 2)
dev.off()

png(paste("~/plot_seurat_",id,threshold,pct_mt,"_Feature_plot_markers_cd4_T_helper_Abdul.png",sep="_"),res = 600,width=12,height=6,units='in')
FeaturePlot(seu, features = c( "Gata3", "Tbx21", "Eomes", "Ccl4", "Ccl5", "Cxcr6"),ncol = 3)
dev.off()
#FeaturePlot
#FeaturePlot(pbmc, features =c("Gzma", "Gzmb", "Gzmh", "Gzmk", "Gzmm", "Prf1", "Nkg7", "Klrd1", "Gnly"),ncol=3)
png(paste("~/plot_seurat",id,threshold,pct_mt,"Feature_plot_markers_cd8_T_cytotoxic_Abdul.png",sep="_"),res = 600,width=12,height=6,units='in')
FeaturePlot(seu, features =c("Gzma", "Gzmb", "Gzmm", "Prf1", "Nkg7", "Klrd1"),ncol=3)
dev.off()

png(paste("~/plot_seurat",id,threshold,pct_mt,"Feature_plot_markers_keratinocytes.png",sep="_"),res = 600,width=12,height=6,units='in')
FeaturePlot(seu, features =c("Krt5","Krt10","Krt14" ,"Ptgs1"),ncol=3)
dev.off()

png(paste("~/plot_seurat",id,threshold,pct_mt,"Feature_plot_markers_epithelial.png",sep="_"),res = 600,width=12,height=6,units='in')
FeaturePlot(seu, features =c("Krt17", "Krt79", "Cd44", "Cd200", "Lrig1"),ncol=2)
dev.off()
```


When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

